Composing Robustly Safe Compilers

### 2023-06-11 popl/main.tex
Change notation of compilers.

\section{Case Study: Memory Safe and Cryptographic Constant Time Code}\label{sec:casestud}
This section defines several secure compilers, each of which robustly preserves a different property of interest.
We demonstrate the power of our framework from \Cref{sec:compprop,sec:compcomp} by composing these compilers for a secure, but optimizing, compilation chain that robustly preserves \gls{ms} and \gls{cct}.
Concretely, \Cref{subsec:cs:tms} starts by defining languages $\src{L_{TMS}}$ and $\trg{L}$ and describes a compiler $\llbracket\src{\bullet}\rrbracket^{\src{L_{TMS}}\to\trg{L}}$ for the robust preservation of \gls{tms} between the two languages.
\Cref{subsec:cs:ms} defines $\irl{L_{MS}}$ and a compiler $\llbracket\trg{\bullet}\rrbracket^{\trg{L}\to\irl{L_{MS}}}$ that robustly preserves \gls{sms}.
By the framework presented in \Cref{sec:compcomp,sec:compprop}, we attain a compiler $\llbracket\src{\bullet}\rrbracket^{\src{L_{TMS}}\to\irl{L_{MS}}}$ for the robust preservation of \gls{ms} by composing $\llbracket\src{\bullet}\rrbracket^{\src{L_{TMS}}\to\trg{L}}$ and $\llbracket\trg{\bullet}\rrbracket^{\trg{L}\to\irl{L_{MS}}}$.
\Cref{subsec:cs:scct} defines $\obj{L_{CCT}}$ and a compiler $\llbracket\irl{\bullet}\rrbracket^{\irl{L_{MS}}\to\obj{L_{CCT}}}$ that robustly preserves \gls{cct}.
Composing it with $\llbracket\src{\bullet}\rrbracket^{\src{L_{TMS}}\to\irl{L_{MS}}}$ yields $\llbracket\src{\bullet}\rrbracket^{\src{L_{TMS}}\to\obj{L_{CCT}}}$, a compiler that robustly preserves a combination of \gls{ms} and \gls{cct}.
We attain our final compilation chain in \Cref{subsec:cs:opts}, which defines optimizing compilers performing either \gls{cf} or \gls{dce} and composes them with $\llbracket\src{\bullet}\rrbracket^{\src{L_{TMS}}\to\obj{L_{CCT}}}$, giving us an optimizing, secure compilation chain.

>>>>

\section{Case Study: Memory Safe and Cryptographic Constant Time Code}\label{sec:casestud}
This section defines several secure compilers, each of which robustly preserves a different property of interest.
We demonstrate the power of our framework from \Cref{sec:compprop,sec:compcomp} by composing these compilers for a secure, but optimizing, compilation chain that robustly preserves \gls{ms} and \gls{cct}.
Concretely, \Cref{subsec:cs:tms} starts by defining languages $\src{L_{TMS}}$ and $\trg{L}$ and describes a compiler $\cc{\src{L_{TMS}}\to\trg{L}}{\src{\bullet}}$ for the robust preservation of \gls{tms} between the two languages.
\Cref{subsec:cs:ms} defines $\irl{L_{MS}}$ and a compiler $\cc{\trg{L}\to\irl{L_{MS}}}{\trg{\bullet}}$ that robustly preserves \gls{sms}.
By the framework presented in \Cref{sec:compcomp,sec:compprop}, we attain a compiler $\cc{\src{L_{TMS}}\to\irl{L_{MS}}}{\src{\bullet}}$ for the robust preservation of \gls{ms} by composing $\cc{\src{L_{TMS}}\to\trg{L}}{\src{\bullet}}$ and $\cc{\trg{L}\to\irl{L_{MS}}}{\trg{\bullet}}$.
\Cref{subsec:cs:scct} defines $\obj{L_{CCT}}$ and a compiler $\cc{\irl{L_{MS}}\to\obj{L_{CCT}}}{\irl{\bullet}}$ that robustly preserves \gls{cct}.
Composing it with $\cc{\src{L_{TMS}}\to\irl{L_{MS}}}{\src{\bullet}}$ yields $\cc{\src{L_{TMS}}\to\obj{L_{CCT}}}{\src{\bullet}}$, a compiler that robustly preserves a combination of \gls{ms} and \gls{cct}.
We attain our final compilation chain in \Cref{subsec:cs:opts}, which defines optimizing compilers performing either \gls{cf} or \gls{dce} and composes them with $\cc{\src{L_{TMS}}\to\obj{L_{CCT}}}{\src{\bullet}}$, giving us an optimizing, secure compilation chain.
